Insert your title here

### 2020-02-12 Article/LaTeX_DL_468198_240419/experimentsInFluids.tex
Journal Format

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\DeclareMathOperator{\sign}{sign}
\usepackage{geometry}
\usepackage{subcaption}
\usepackage{standalone}
\usepackage{xcolor}
\usepackage{enumitem}
\setlist{nosep}

@@

\addbibresource{articleBOS.bib}
\begin{document}
\today
\section{Abstract}

\section{Introduction}
The Background Oriented Schlieren technique (BOS) is an optical density visualization technique \cite{meier2002computerized,raffel2015background}. First described in \cite{dalziel2000whole}, where it was called Synthetic Schlieren (SS). This technique provides whole-field measurements of density gradients. One of the strengths of this technique was the simplicity of the experimental setup. Parts of the traditional, more extensive optical setups were replaced by digital image analysis.

@@

\printbibliography[heading=bibintoc]

%\appendix

%\section{Runge-Kutta Scheme}
%\label{app:RKS}
%We choose a step size $h$. These are steps over the arc-length $s$. We use an index $p$ to indicate each step: $s^{p+1} = s^{p} + h$.

%\subsubsection{Rotation Matrix}
%\label{subsubsec:rotmat}
%{\color{red} Work in Progress, you can skip this} \\
%A rotation through an angle of $\theta$ around an axis defined by the unit vector $\underline{\hat{r}} = r_x \underline{\hat{i}} + r_y \underline{\hat{j}} + r_z \underline{\hat{k}}$ can be represented by a quaternion
%\begin{equation}
%	\underline{q} = \cos\frac{\theta}{2} + (r_x \underline{\hat{i}} + r_y \underline{\hat{j}} + r_z \underline{\hat{k}} ) \sin \frac{\theta}{2}.
%\end{equation} 
%A unit quaternion has norm one. The rotation matrix $Q$ for a unit quaternion $\underline{q} = q_0 + q_1 \underline{\hat{i}} + q_2 \underline{\hat{j}} + q_3 \underline{\hat{k}}$ is
%\begin{equation}
%	Q = \left[ \begin{array}{ccc} 1-2(q_2^2+q_3^2) & 2(q_1 q_2 - q_0 q_3) & 2(q_1 q_3 + q_0 q_2) \\ 2 (q_1 q_2 + q_0 q_3) & 1-2(q_1^2+q_3^2) & 2( q_2 q_3 - q_0 q_1) \\ 2(q_1 q_3-q_0 q_2) & 2 (q_2 q_3 + q_0 q_1) & 1 - 2 (q_1^2+q_2^2) \end{array} \right]
%\end{equation}

%The rotation angle is
%\begin{equation}
%	\cos \theta = a \cdot 0 + b \cdot 0 + c \cdot 1
%\end{equation}
%and the rotation vector
%\begin{equation}
%	\underline{\hat{r}} = - \frac{b}{\sqrt{a^2+b^2}} \underline{\hat{i}} + \frac{a}{\sqrt{a^2+b^2}}  \underline{\hat{j}} + 0  \underline{\hat{k}}.
%\end{equation}

%\subsubsection{Intersection Light Rays and Planes: Inhomogeneous medium}
%{\color{red} Work in Progress, you can skip this} \\
%A light ray traveling through an inhomogeneous medium does not travel in a straight line. The path is governed by (\ref{eq:sys6foeq}). To simplify (\ref{eq:sys6foeq}), we can use that there is a direction in the experimental setup that has no variation in index of refraction $n$, which is the direction of the unit normal of the different planes. To use this simplification, we want to transform our direction cosines in our original coordinate system, $xyz$ into direction cosines in a new coordinate system, $XYZ$. In this new coordinate system, the $Z$-axis is opposite to the unit normal vector $\underline{\hat{n}}$. To find this transformation matrix, we use quaternions.

%\subsubsection{Procedure Varying n}
%{\color{red} Work in Progress, you can skip this} \\
%Given $n(x,y)$. Old coordinates: x,y,z. New coordinates u,v,w.
%\begin{enumerate}
%	\item Determine Coordinate Transformation according to \ref{subsubsec:rotmat}. \\
%	\item Transform Initial Position to new coordinates u,v  \\
%	\item Initiate n field in new coordinates u,v \\
%	\item  Apply Snell's Law in old coordinates (x,y,z) using the new n(u,v) \\
%	\item Transform Refracted Rays to new coordinates u, v, w \\
%	\item  Runge-Kutta \\
%	\item  Obtain grad n = ( dn/du, dn/dv, dn/dw) \\
%	\item  Transform incoming rays back to coordinates x y z \\
%	\item  Apply Snell's Law in old coordinates (x,y,z) using the new n(u,v) \\
%	\item Transform Final Positions to new old coordinates x, y, z \\
%\end{enumerate}

\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{subcaption}
\usepackage{standalone}
\usepackage{xcolor}
\usepackage{enumitem}
\setlist{nosep}

@@

\addbibresource{articleBOS.bib}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
\DeclareMathOperator{\sign}{sign}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Insert your title here%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
\subtitle{Do you have a subtitle?\\ If so, write it here}

%\titlerunning{Short form of title}        % if too long for running head

\author{Alexander M. van Oers \and
       Leo R.M. Maas %etc.
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{Alexander M. van Oers \at
              first address \\
              Tel.: +123-45-678910\\
              Fax: +123-45-678910\\
              \email{fauthor@example.com}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           Leo R.M. Maas \at
              second address
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
Insert your abstract here. Include keywords, PACS and mathematical
subject classification numbers as needed.
\keywords{First keyword \and Second keyword \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\label{intro}
The Background Oriented Schlieren technique (BOS) is an optical density visualization technique \cite{meier2002computerized,raffel2015background}. First described in \cite{dalziel2000whole}, where it was called Synthetic Schlieren (SS). This technique provides whole-field measurements of density gradients. One of the strengths of this technique was the simplicity of the experimental setup. Parts of the traditional, more extensive optical setups were replaced by digital image analysis.

@@

\begin{acknowledgements}
If you'd like to thank anyone, place your comments here
and remove the percent signs.
\end{acknowledgements}

\section*{Funding}

\section*{Availability of data and material}

\section*{Code availability}
% Authors must disclose all relationships or interests that 
% could have direct or potential influence or impart bias on 
% the work: 
%
 \section*{Conflict of interest}
 The authors declare that they have no conflict of interest.

\printbibliography[heading=bibintoc]
% BibTeX users please use one of
%\bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
%\bibliography{}   % name your BibTeX data base

% Non-BibTeX users please use
%\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
%\bibitem{RefJ}
% Format for Journal Reference
%Author, Article title, Journal, Volume, page numbers (year)
% Format for books
%\bibitem{RefB}
%Author, Book title, page numbers. Publisher, place (year)
% etc
%\end{thebibliography}

\end{document}
% end of file template.tex
